Highly Available Transactions: Virtues and Limitations

### 2013-05-01 writeup/evaluation.tex
PB more

When we deployed five clusters (as opposed to two, as before) across
the five AWS datacenters with lowest communication cost
(Figure~\ref{fig:wan-exp}C), the trend continues: mastered latency
increases to nearly $800$ms per transaction. As an attempt at reducing
this overhead, we implemented and benchmarked a variant of
quorum-based replication as in Dynamo~\cite{dynamo}, where clients
sent requests to all replicas, which completed as soon as a majority
of servers responded (guaranteeing regular
semantics~\cite{herlihy-art}); this strategy (not pictured) did not
substantially improve performance due to the network topology and
because worst-case server load was unaffected. With five clusters,
TA's relative throughput decreased: every YCSB \texttt{put} operation
resulted in four \texttt{put} operations on remote replicas and,
accordingly, the cost of anti-entropy increased (e.g., each server
processed four incoming anti-entropy streams---as opposed to one
before---reducing the opportunity for batching and decreasing
available resources for for incoming client requests). This in turn
increased garbage collection activity and, more importantly, IOPS when
compared to Eventual and RC, causing TA throughput to peak at around half
of Eventual. With an in-memory persistence (i.e., no LevelDB or WAL),
TA throughput was within 20\% of eventual.

@@

\vspace{.5em}\noindent\textit{Read proportion.} Our default (equal)
proportion of reads and writes is fairly pessimistic: for example,
Facebook reports $99.8\%$ reads for their workload~\cite{eiger}. As
shown in Figure~\ref{fig:rprop} (clusters in Virginia and Oregon),
with all reads, TA is within $4.8\%$ of eventual; with all writes, TA
is within $33\%$, and Eventual throughput decreases by $288.8\%$
compared to all reads and TA is within $33\%$ of eventual. At $99.8\%$
reads, TA incurs a $7\%$ overhead ($5.8\%$ for in-memory storage).

>>>>

When we deployed five clusters (as opposed to two, as before) across
the five EC2 datacenters with lowest communication cost
(Figure~\ref{fig:wan-exp}C), the trend continues: mastered latency
increases to nearly $800$ms per transaction. As an attempt at reducing
this overhead, we implemented and benchmarked a variant of
quorum-based replication as in Dynamo~\cite{dynamo}, where clients
sent requests to all replicas, which completed as soon as a majority
of servers responded (guaranteeing regular
semantics~\cite{herlihy-art}); this strategy (not pictured) did not
substantially improve performance due to the network topology and
because worst-case server load was unaffected. With five clusters,
TA's relative throughput decreased: every YCSB \texttt{put} operation
resulted in four \texttt{put} operations on remote replicas and,
accordingly, the cost of anti-entropy increased (e.g., each server
processed four replica's anti-entropy as opposed to one before,
reducing the opportunity for batching and decreasing available
resources for for incoming client requests). This in turn increased
garbage collection activity and, more importantly, IOPS when compared
to Eventual and RC, causing TA throughput to peak at around half of
Eventual. With an in-memory persistence (i.e., no LevelDB or WAL), TA
throughput was within 20\% of eventual.

@@

\vspace{.5em}\noindent\textit{Read proportion.} Our default (equal)
proportion of reads and writes is fairly pessimistic: for example,
Facebook reports $99.8\%$ reads for their workload~\cite{eiger}. As
shown in Figure~\ref{fig:rprop} (clusters in Virginia and Oregon),
with all reads, TA is within $4.8\%$ of eventual; with all writes, TA
is within $33\%$, and the throughput of eventual consistency decreases
by $288.8\%$ compared to all reads. At $99.8\%$ reads, TA incurs a $7\%$ overhead ($5.8\%$ for
in-memory storage).

### 2013-05-01 writeup/hat-analysis.tex
PB more

\vspace{.5em}\noindent\textbf{{Monotonic reads}} requires that, within
a session, subsequent reads to a given object ``never return any
previous values''; reads from each item progress according to a total
order. The ordering of reads should respect any externally observable
total ordering on transactions.

@@

\begin{table}[t!]
\begin{tabular}{| c | p{6cm} | }\hline
HA & Transactional Atomicity (TA), Read Uncommitted (RU), Read
Committed (RC), Item Cut Isolation (I-CI), Predicate Cut Isolation
(P-CI), Monotonic Reads (MR), Monotonic Writes (MW), Writes Follow
Reads (WFR)\\\hline Sticky-HA & Read Your Writes (RYW), PRAM,
Causal\\\hline Unavailable & Cursor Stability (CS)\lostupdate,
Snapshot Isolation (SI)\lostupdate, Repeatable Read
(RR)\lostupdate\rwskew, One-Copy Serializability
(1SR)\lostupdate\rwskew, Recency\linearizable, Safe\linearizable,
Regular\linearizable, Linearizability\linearizable, Strong
1SR\lostupdate\rwskew\linearizable \\\hline
\end{tabular}
\caption{Summary of highly available, sticky highly available, and
  unavailable models considered in this paper. Unavailable models are
  labeled by cause of unavailability: preventing lost
  update\lostupdate, preventing write skew\rwskew, and requiring
  recency guarantees\linearizable.}\vspace{-.5em}
\label{table:hatcompared}
\end{table}

>>>>

\vspace{.5em}\noindent\textbf{{Monotonic reads}} requires that, within
a session, subsequent reads to a given object ``never return any
previous values''; reads from each item progress according to a total
order. The ordering of versions read should respect any ordering on
transactions.

@@

\begin{table}[t!]
\begin{tabular}{| c | p{6cm} | }\hline
HA & Transactional Atomicity (TA), Read Uncommitted (RU), Read
Committed (RC), Item Cut Isolation (I-CI), Predicate Cut Isolation
(P-CI), Monotonic Reads (MR), Monotonic Writes (MW), Writes Follow
Reads (WFR)\\\hline Sticky-HA & Read Your Writes (RYW), PRAM,
Causal\\\hline Unavailable & Cursor Stability (CS)\lostupdate,
Snapshot Isolation (SI)\lostupdate, Repeatable Read
(RR)\lostupdate\rwskew, One-Copy Serializability
(1SR)\lostupdate\rwskew, Recency\linearizable, Safe\linearizable,
Regular\linearizable, Linearizability\linearizable, Strong
1SR\lostupdate\rwskew\linearizable \\\hline
\end{tabular}
\caption{Summary of highly available, sticky highly available, and
  unavailable models considered in this paper. Unavailable models are
  labeled by cause of unavailability: preventing lost
  update\lostupdate, preventing write skew\rwskew, and requiring
  recency guarantees\linearizable.}
\label{table:hatcompared}
\end{table}
